---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master) -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/fwildclusterboot)](https://CRAN.R-project.org/package=fwildclusterboot) -->
<!-- ![runiverse-package](https://s3alfisc.r-universe.dev/badges/fwildclusterboot) -->
<!-- [![R-CMD-check](https://github.com/s3alfisc/fwildclusterboot/workflows/R-CMD-check/badge.svg)](https://github.com/s3alfisc/fwildclusterboot/actions) -->
<!-- [![Codecov test coverage](https://codecov.io/gh/s3alfisc/fwildclusterboot/branch/master/graph/badge.svg)](https://app.codecov.io/gh/s3alfisc/fwildclusterboot?branch=master) -->
<!-- `r badger::badge_cran_download("fwildclusterboot", "grand-total", "blue")` -->
<!-- `r badger::badge_cran_download("fwildclusterboot", "last-month", "green")` -->
<!-- [![minimal R version](https://img.shields.io/badge/R%3E%3D-4.0.0-6666ff.svg)](https://cran.r-project.org/) -->

<!-- badges: end -->

# wildboottestjlr

`wildboottestjlr` ports the functionality of the [WildBootTests.jl](https://github.com/droodman/WildBootTests.jl) package to R via the `JuliaConnectoR` package. 

At the moment, it supports the following features of `WildBootTests.jl`:


+ The wild bootstrap for OLS (Wu 1986).
+ The Wild Restricted Efficient bootstrap (WRE) for IV/2SLS/LIML (Davidson and MacKinnon 2010).
+ The subcluster bootstrap (MacKinnon and Webb 2018).
+ Confidence intervals formed by inverting the test and iteratively searching for bounds.
+ Multiway clustering.
+ Arbitrary and multiple linear hypotheses in the parameters.
+ One-way fixed effects.

The following model objects are currently supported: 

+ OLS: `lm` (from stats), `fixest` (from fixest), `felm` from (felm)
+ IV: `ivreg` (from ivreg). 

In the future, IV methods for `fixest` and `lfe` will be added.


## Installation / Getting Started

`wildboottestjlr` can be installed by running

```{r, eval = FALSE}
library(devtools)
install_github("s3alfisc/wildboottestjlr")
```

You can install Julia by following the steps described here: https://julialang.org/downloads/. `WildBootTests.jl` can be installed via 
Julia's package management system. 

To install R and Julia from within R, you can use functionality from `JuliaCall`:

```{r, eval = FALSE}
library(JuliaCall)
wildboottestjlr::wildboottestjlr_setup(install_julia = TRUE, 
                                       install_wildboottests = TRUE)

```


## Example 

`wildboottestjlr's` central function is `boottest()`. Beyond few minor differences, it largely mirrors the `boottest()` function from the `fwildclusterboot` package.

### The Wild Bootstrap for OLS

```{r, message = FALSE, warning = FALSE}
# set a 'global' seed in the Julia session
library(wildboottestjlr)

set_julia_seed(rng = 12313452435)

data(voters)
library(fixest)
library(lfe)

# estimation via lm(), fixest::feols() or lfe::felm()
lm_fit <- lm(proposition_vote ~ treatment  + log_income, data = voters)
feols_fit <- feols(proposition_vote ~ treatment  + log_income, data = voters)
felm_fit <- felm(proposition_vote ~ treatment  + log_income, data = voters)

boot_lm <- boottest(lm_fit, clustid = "group_id1", B = 999, param = "treatment", rng = 7651427)
boot_feols <- boottest(feols_fit, clustid = "group_id1", B = 999, param = "treatment", rng = 7651427)
boot_felm <- boottest(felm_fit, clustid = "group_id1", B = 999, param = "treatment", rng = 7651427)

# summarize results via summary() method
#summary(boot_lm)

# also possible: use msummary() from modelsummary package
library(modelsummary)
msummary(list(boot_lm, boot_feols, boot_felm), 
        estimate = "{estimate} ({p.value})", 
        statistic = "[{conf.low}, {conf.high}]"
        )  
```

### The Wild Bootstrap for IV (WRE)

If `boottest()` is applied based on an object of type `ivreg`, the WRE bootstrap [Davidson & MacKinnon (2010)](https://www.tandfonline.com/doi/abs/10.1198/jbes.2009.07221) is run. 

```{r, message = FALSE, warning = FALSE}
library(ivreg)
data("SchoolingReturns", package = "ivreg")
data <- SchoolingReturns

ivreg_fit <- ivreg(log(wage) ~ education + age + ethnicity + smsa + south + parents14 |
                  nearcollege + age  + ethnicity + smsa + south + parents14,
                data = data)

boot_ivreg <- boottest(object = ivreg_fit, B = 999, param = "education", clustid = "fameducation", type = "webb")

summary(boot_ivreg)
```



